```{r}
library(sf)
library(tidygraph)
library(tidyverse)
library(reshape)
library(tmap)
library(reshape2)
library(writexl)
library(readxl)
library(sp)
library(biglm)
library(broom)
library(heatmaply)
```
# Road Distances
Road distances were computed with ArcGis as R would not function for some reason.
```{r}
SA1.dist <- read.csv("D:/Users/z3531028/OneDrive - UNSW/Data/Census/netdist_sa1_szn.csv")
SA1.dist <- SA1.dist %>% 
  select(Name, Total_Leng)

OD <- strsplit(SA1.dist$Name, " - ")
od.mat <- matrix(unlist(OD), ncol=2, byrow=TRUE)
od.df <- as.data.frame(od.mat)
od.df$Distance <- SA1.dist$Total_Leng
od.df$Distance <- od.df$Distance/1000
od.df <- od.df %>% 
  rename(Origin = V1,
         Destination = V2)

rm(OD)
rm(od.mat)
rm(SA1.dist)
```

# 2016 Journey to Work
```{r}
emp_mat.16 <- read.csv("./Data/GS_2016_JourneyToWork.csv")
emp_mat.16 <- as.matrix(emp_mat.16)
rownames(emp_mat.16) <- emp_mat.16[,1]
emp_mat.16 <- emp_mat.16[,2:2234]
emp_df.16 <- melt(emp_mat.16)

emp_df.16 <- emp_df.16 %>% 
  dplyr::rename(Origin = Var1,
         Destination = Var2,
         Flow = value)
emp_df.16$Destination <- substring(emp_df.16$Destination, 2)
emp_df.16 <- emp_df.16 %>% 
  arrange(Origin)
```

# 2011 Journey to Work
```{r}
emp_mat.11 <- read_xlsx("./Data/GS_2011_JourneyToWork.xlsx")
emp_mat.11 <- as.matrix(emp_mat.11)
rownames(emp_mat.11) <- emp_mat.11[,1]

emp_mat.11 <- emp_mat.11[,2:3644]
emp_df.11 <- melt(emp_mat.11)

emp_df.11 <- emp_df.11 %>% 
  dplyr::rename(Origin = Var1,
         Destination = Var2,
         Flow = value)
emp_df.11 <- emp_df.11 %>% 
  arrange(Origin)

emp_df.11$Origin <- as.character(emp_df.11$Origin)
emp_df.11$Destination <- as.character(emp_df.11$Destination)
```

# Getting XY Coords
```{r}
sa1_shp <- st_read("./Data/shapes/SA1_Centre_Mass.shp")
sa1.xy <- as.data.frame(st_coordinates(sa1_shp))
sa1.area <- st_read("./Data/shapes/SYD_SA1_Census_2016.shp")
sa1.area <-  sa1.area %>% 
  select(SA1_7DIG16, AREASQKM16) %>% 
  st_drop_geometry() %>% 
  dplyr::rename(Origin = SA1_7DIG16,
                SA1_Area = AREASQKM16)
                    
sa1_df <- sa1_shp %>% 
  select(SA1_7DIG16) %>% 
  mutate(Origin = SA1_7DIG16,
    Origin.X = sa1.xy$X,
         Origin.Y = sa1.xy$Y) %>% 
  select(-SA1_7DIG16) %>% 
  st_drop_geometry() 

sa1_df <- sa1_df %>% 
  inner_join(sa1.area)

dzn_shp <- st_read("./Data/shapes/DZN_Centre_Mass.shp")
dzn.xy <- as.data.frame(st_coordinates(dzn_shp))
dzn.area <- st_read("./Data/shapes/GS_DZN_shape.shp")
dzn.area <- dzn.area %>% 
  select(DZN_CODE16,AREASQKM16) %>% 
  st_drop_geometry() %>% 
  dplyr::rename(Destination = DZN_CODE16,
                DZN_Area = AREASQKM16)

dzn_df <- dzn_shp %>% 
  select(DZN_CODE16) %>% 
  mutate(Destination.X = dzn.xy$X,
         Destination.Y = dzn.xy$Y) %>% 
  dplyr::rename(Destination = DZN_CODE16) %>% 
  st_drop_geometry()

dzn_df <- dzn_df %>% 
  inner_join(dzn.area)

rm(dzn_shp)
rm(sa1_shp)
```

# Adding Coordinates to Emp Database
```{r}
emp_df.16 <- emp_df.16 %>% 
  inner_join(sa1_df, by = "Origin") %>% 
  inner_join(dzn_df, by = "Destination")

emp_df.11 <- emp_df.11 %>% 
  inner_join(sa1_df, by = "Origin") %>% 
  inner_join(dzn_df, by = "Destination")
```

# Setting Origin and Destination Totals
```{r}
emp_df.16$Flow <- as.numeric(emp_df.16$Flow)

Origin_Total.16 <- aggregate(emp_df.16$Flow, by=list(Origin = emp_df.16$Origin), FUN = sum)
Destination_Total.16 <- aggregate(emp_df.16$Flow, by=list(Destination = emp_df.16$Destination), FUN = sum)

emp_df.16 <- emp_df.16 %>%
  inner_join(Origin_Total.16, by = "Origin") %>% 
  inner_join(Destination_Total.16, by = "Destination") %>% 
  dplyr::rename(Origin_Total = x.x,
                Destination_Total = x.y)

emp_df.11$Flow <- as.numeric(emp_df.11$Flow)

Origin_Total.11 <- aggregate(emp_df.11$Flow, by=list(Origin = emp_df.11$Origin), FUN = sum)
Destination_Total.11 <- aggregate(emp_df.11$Flow, by = list(Destination = emp_df.11$Destination), FUN = sum)

emp_df.11 <- emp_df.11 %>%
  inner_join(Origin_Total.11, by = "Origin") %>% 
  inner_join(Destination_Total.11, by = "Destination") %>% 
  dplyr::rename(Origin_Total = x.x,
                Destination_Total = x.y)
```

# Adding Distance Variables
Adding road network distance

```{r}
emp_df.16 <- emp_df.16 %>% 
  inner_join(od.df, by = c("Origin", "Destination"))
emp_df.11 <- emp_df.11 %>% 
  inner_join(od.df, by = c("Origin", "Destination"))
```

The code below is a faster way; but it is Euclidean if there is not enough memory to run network query
```{r eval=FALSE, include=FALSE}
O_t.16 <- emp_df.16 %>% 
  select(Origin, Origin.X, Origin.Y)
O_t.16 <- O_t.16 %>% distinct(Origin, .keep_all = T)
O_t.16 <-  st_as_sf(O_t.16, coords = c('Origin.X', 'Origin.Y'), crs = st_crs(4326))

D_t.16 <- emp_df.16 %>% 
  select(Destination, Destination.X, Destination.Y)
D_t.16 <- D_t.16 %>% distinct(Destination, .keep_all = T)
D_t.16 <-   st_as_sf(D_t.16, coords = c('Destination.X', 'Destination.Y'), crs = st_crs(4326))

O_t.16 <- as(O_t.16, "Spatial")
D_t.16 <- as(D_t.16, "Spatial")

dist_mat.16 <- spDists(O_t.16,D_t.16)
dist_pair.16 <- melt(dist_mat.16)
emp_df.16$Distance <- dist_pair.16$value

O_t.11 <- emp_df.11 %>% 
  select(Origin, Origin.X, Origin.Y)
O_t.11 <- O_t.11 %>% distinct(Origin, .keep_all = T)
O_t.11 <-  st_as_sf(O_t.11, coords = c('Origin.X', 'Origin.Y'), crs = st_crs(4326))

D_t.11 <- emp_df.11 %>% 
  select(Destination, Destination.X, Destination.Y)
D_t.11 <- D_t.11 %>% distinct(Destination, .keep_all = T)
D_t.11 <-   st_as_sf(D_t.11, coords = c('Destination.X', 'Destination.Y'), crs = st_crs(4326))

O_t.11 <- as(O_t.11, "Spatial")
D_t.11 <- as(D_t.11, "Spatial")
dist_mat.11 <- spDists(O_t.11,D_t.11)
dist_pair.11 <- melt(dist_mat.11)
emp_df.11$Distance <- dist_pair.11$value
```

# Spatial Interaction
# generalised accessibility

## r-square function
```{r}
CalcRSquared <- function(observed,estimated){
  r <- cor(observed,estimated)
  R2 <- r^2
  R2
}
```

# beta 
```{r}
options(scipen = 1000)
beta.16 <- -2.201457
alpha.16 <- 0.4022

emp_ai.16 <- emp_df.16 %>% 
  select(Origin, Destination, Flow, Origin_Total, Destination_Total, SA1_Area, DZN_Area, Distance) %>% 
  filter(Flow != 0)

emp_ai.16 <- emp_ai.16 %>% 
  mutate(f_dij = exp(beta.16 * Distance)) %>% 
  mutate(Est_Cost = 1-f_dij) %>% 
  mutate(ai = (Destination_Total)^alpha.16 * f_dij)

emp_a.16 <- emp_ai.16 %>% 
  select(Origin, ai)

emp_Ai.16 <- aggregate(emp_a.16$ai, by=list(Origin = emp_a.16$Origin), FUN = sum)
emp_Ai.16 <- emp_Ai.16 %>% 
  dplyr::rename(x_Ai = x)

emp_ai.16 <- emp_ai.16 %>% 
  inner_join(emp_Ai.16) %>% 
  mutate(Ai = 1/x_Ai)

emp_ai.16 <- emp_ai.16 %>% 
  mutate(est_flow = (Origin_Total) * (Destination_Total^alpha.16) * Ai * f_dij) %>% 
  mutate(Potential = (Destination_Total)/f_dij) %>% 
  mutate(Normalised_Potential = normalize(Potential))

CalcRSquared(emp_ai.16$Flow,emp_ai.16$est_flow)

write.csv(emp_ai.16, "D:/Users/z3531028/OneDrive - UNSW/Data/Census/2016/Demographic/accessibility_16.csv")
```

```{r}
Origin_Total.11 <- aggregate(emp_df.11$Flow, by=list(Origin = emp_df.11$Origin), FUN = sum)
Destination_Total.11 <- aggregate(emp_df.11$Flow, by = list(Destination = emp_df.11$Destination), FUN = sum)
```

```{r}
beta.11 <- -1.98785
alpha.11 <- 0.325

emp_ai.11 <- emp_df.11 %>% 
  select(Origin, Destination, Flow, Origin_Total, Destination_Total, SA1_Area, DZN_Area, Distance) %>% 
  filter(Flow != 0)

emp_ai.11 <- emp_ai.11 %>% 
  mutate(f_dij = exp(beta.11*Distance)) %>% 
  mutate(Est_Cost = 1-f_dij) %>% 
  mutate(ai = (Destination_Total^alpha.11) * f_dij)

emp_a.11 <- emp_ai.11 %>% 
  select(Origin, ai)

emp_Ai.11 <- aggregate(emp_a.11$ai, by=list(Origin = emp_a.11$Origin), FUN = sum)
emp_Ai.11 <- emp_Ai.11 %>% 
  dplyr::rename(x_Ai = x)

emp_ai.11 <- emp_ai.11 %>% 
  inner_join(emp_Ai.11) %>% 
  mutate(Ai = 1/x_Ai)

emp_ai.11 <- emp_ai.11 %>% 
  mutate(est_flow = (Origin_Total) * ((Destination_Total^alpha.11)) * Ai * f_dij) %>% 
  mutate(Potential = (Destination_Total)/f_dij) %>% 
  mutate(Normalised_Potential = normalize(Potential))

sa1_Ai.11 <- aggregate(emp_ai.11$Normalised_Potential, by=list(Origin = emp_ai.11$Origin), FUN = sum)

CalcRSquared(emp_ai.11$Flow,emp_ai.11$est_flow)

write.csv(sa1_Ai.11, "D:/Users/z3531028/OneDrive - UNSW/Data/Census/2016/Demographic/accessibility_11.csv")

```

## Calibrating beta

```{r}
emp_df.16 <- as.data.frame(emp_df.16)
emp_df.16$Origin <- as.factor(emp_df.16$Origin)

emp_df.11 <- as.data.frame(emp_df.11)
emp_df.11$Origin <- as.factor(emp_df.11$Origin)
```

```{r}
rm(list=setdiff(ls(), c("emp_df.11", "emp_df.16")))
```

```{r}
emp_df.16.t <- emp_df.16 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.16 <- glm(Flow ~ Origin + 
                     log(Origin_Total) + 
                           log((Destination_Total)) + 
                           log(Distance) - 1, 
                   data = emp_df.16.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.16.a <- tidy(sim.16)

emp_df.11.t <- emp_df.11 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.11 <- glm(Flow ~ Origin + 
                log((Origin_Total)) +
                log((Destination_Total)) + 
                log(Distance) - 1, 
                   data = emp_df.11.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.11.a <- tidy(sim.11)

```

```{r}

emp_df.16.t <- emp_df.16 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.16 <- glm(Flow ~ Origin + 
                     log(Origin_Total) + 
                           log((Destination_Total)) + 
                           log(Distance) - 1, 
                   data = emp_df.16.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.16.b <- tidy(sim.16)

emp_df.11.t <- emp_df.11 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.11 <- glm(Flow ~ Origin + 
                log((Origin_Total)) +
                log((Destination_Total)) + 
                log(Distance) - 1, 
                   data = emp_df.11.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.11.b <- tidy(sim.11)

```

```{r}

emp_df.16.t <- emp_df.16 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.16 <- glm(Flow ~ Origin + 
                     log(Origin_Total) + 
                           log((Destination_Total)) + 
                           log(Distance) - 1, 
                   data = emp_df.16.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.16.c <- tidy(sim.16)

emp_df.11.t <- emp_df.11 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.11 <- glm(Flow ~ Origin + 
                log((Origin_Total)) +
                log((Destination_Total)) + 
                log(Distance) - 1, 
                   data = emp_df.11.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.11.c <- tidy(sim.11)

```

```{r}

emp_df.16.t <- emp_df.16 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.16 <- glm(Flow ~ Origin + 
                     log(Origin_Total) + 
                           log((Destination_Total)) + 
                           log(Distance) - 1, 
                   data = emp_df.16.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.16.d <- tidy(sim.16)

emp_df.11.t <- emp_df.11 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.11 <- glm(Flow ~ Origin + 
                log((Origin_Total)) +
                log((Destination_Total)) + 
                log(Distance) - 1, 
                   data = emp_df.11.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.11.d <- tidy(sim.11)

```

```{r}

emp_df.16.t <- emp_df.16 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.16 <- glm(Flow ~ Origin + 
                     log(Origin_Total) + 
                           log((Destination_Total)) + 
                           log(Distance) - 1, 
                   data = emp_df.16.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.16.e <- tidy(sim.16)

emp_df.11.t <- emp_df.11 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.11 <- glm(Flow ~ Origin + 
                log((Origin_Total)) +
                log((Destination_Total)) + 
                log(Distance) - 1, 
                   data = emp_df.11.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.11.e <- tidy(sim.11)

```

```{r}

emp_df.16.t <- emp_df.16 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.16 <- glm(Flow ~ Origin + 
                     log(Origin_Total) + 
                           log((Destination_Total)) + 
                           log(Distance) - 1, 
                   data = emp_df.16.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.16.f <- tidy(sim.16)

emp_df.11.t <- emp_df.11 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.11 <- glm(Flow ~ Origin + 
                log((Origin_Total)) +
                log((Destination_Total)) + 
                log(Distance) - 1, 
                   data = emp_df.11.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.11.f <- tidy(sim.11)

```

```{r}

emp_df.16.t <- emp_df.16 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.16 <- glm(Flow ~ Origin + 
                     log(Origin_Total) + 
                           log((Destination_Total)) + 
                           log(Distance) - 1, 
                   data = emp_df.16.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.16.g <- tidy(sim.16)

emp_df.11.t <- emp_df.11 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.11 <- glm(Flow ~ Origin + 
                log((Origin_Total)) +
                log((Destination_Total)) + 
                log(Distance) - 1, 
                   data = emp_df.11.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.11.g <- tidy(sim.11)

```

```{r}

emp_df.16.t <- emp_df.16 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.16 <- glm(Flow ~ Origin + 
                     log(Origin_Total) + 
                           log((Destination_Total)) + 
                           log(Distance) - 1, 
                   data = emp_df.16.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.16.h <- tidy(sim.16)

emp_df.11.t <- emp_df.11 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.11 <- glm(Flow ~ Origin + 
                log((Origin_Total)) +
                log((Destination_Total)) + 
                log(Distance) - 1, 
                   data = emp_df.11.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.11.h <- tidy(sim.11)

```

```{r}

emp_df.16.t <- emp_df.16 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.16 <- glm(Flow ~ Origin + 
                     log(Origin_Total) + 
                           log((Destination_Total)) + 
                           log(Distance) - 1, 
                   data = emp_df.16.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.16.i <- tidy(sim.16)

emp_df.11.t <- emp_df.11 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.11 <- glm(Flow ~ Origin + 
                log((Origin_Total)) +
                log((Destination_Total)) + 
                log(Distance) - 1, 
                   data = emp_df.11.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.11.i <- tidy(sim.11)

```

```{r}

emp_df.16.t <- emp_df.16 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.16 <- glm(Flow ~ Origin + 
                     log(Origin_Total) + 
                           log((Destination_Total)) + 
                           log(Distance) - 1, 
                   data = emp_df.16.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.16.j <- tidy(sim.16)

emp_df.11.t <- emp_df.11 %>% 
  filter(Origin_Total != 0,
         Destination_Total != 0,
         SA1_Area != 0,
         DZN_Area != 0) %>% 
  sample_n(5000)

sim.11 <- glm(Flow ~ Origin + 
                log((Origin_Total)) +
                log((Destination_Total)) + 
                log(Distance) - 1, 
                   data = emp_df.11.t, 
                   na.action = na.exclude, 
                   family = poisson(link = 'log'))

sim.11.j <- tidy(sim.11)

```
